\chapter{Requirements}

    There are a lot of problems that they are facing, in order to build the system to surveil and follow the patient who have disease under surveillance and make policy decision, we are invited to be in the same team to help the ministry of public health to build Epidemic Intelligent Information System(EIIS). We went to discuss with the team in order to understand the overall situations and gather the requirements. There are six main requirements that they need which are at a glance report, demographics report, lab-upload function, and upload status page, individual report and workload report. 
    
\section{At a glance Report}
    In this requirement, they want the system to show the a glance report page which will show the report that they can surveil and follow the patient in order to control and prevent diseases under surveillance.
    In order to see how at a glance report work, you can see activity diagram in chapter two in  \ref{glance-report}, and also can see the user interface of at a glance report in \ref{at-a-glance-report}.
    % example to see the table

        
\section{Demographics Report}
    In this requirement, they also want a demographics report page that will show the summary of the data that come in to this system. For example nationality pie chart, occupation pie chart, sex pie chart, and so on. The example of the chart is in \ref{demographics_report}. In addition, you can see all the steps in order to see demographics report in chapter two in section \ref{demographics_report_sec}, and also can see the activity diagram in figure \ref{demographics}
        
\section{Upload}
% upload what file?
    Uploading the file is one requirement that they want in this system because they want every hospital can upload file and send to the system. The example of user interface design is show in section \ref{upload_file} in figure between \ref{upload-status1} and \ref{upload-status3} . Furthermore, all the steps to see how to upload is show in section \ref{upload_file_activity_diagram} in figure \ref{upload}

\section{Checking Upload Status}
    Since they want upload function then checking upload status is the require too in order for them to check the status of the uploading file. Checking upload status means that they can check that which month that they are not sending the file, so they can upload the missing file. The example of user interface design is show in section \ref{check_upload_history_status_ui}. Furthermore, all the steps to see how to upload is show in \ref{check_upload_status_activity_diagram}
    
\section{Individual Report}
    In this requirement, they want the system to show the individual report that will they can see the report of each patient in their hospital. Only that disease coordinator in each hospital can see their own patient individual report. From this report they want to check whether the patient still receive drug or not and where the patient are. This will help them to keep track of the patient even thought the patient went to another hospital but his/her is still alive. Moreover, they also want to see the status of the patient where the condition of the disease are getting worse or better from the level of CD4 and viral load. Furthermore, all the steps to see individual report is show in \ref{individual_report_activity_diagram}
    
\section{Workload Report}
    Workload report is one of requirement that they want the system to be able to show.This report need to be able to show how many patient who come to hospital in certain diseases of choosing period of time. The reason they want this report is to minimise and maximise the workload they will have in the future and to be able to estimate the budget need to invest in the drug.Furthermore, all the steps to see workload report is show in \ref{workload_report_activity_diagram}